### 2023-07-17 Article_PySF.tex
hcni update Article_PySF.tex

{\bf \noindent PROGRAM SUMMARY} \\
\begin{small}
\noindent
{\em Program Title:} PyStructureFactor \\
{\em CPC Library link to program files:} (to be added by Technical Editor) \\
{\em Developer's repository link:} \url{https://github.com/TheStarAlight/PyStructureFactor} \\
{\em Code Ocean capsule:} (to be added by Technical Editor) \\
{\em Licensing provisions:} Apache-2.0 \\
{\em Programming language:} Python 3                                  \\
{\em Supplementary material:}                                 \\
{\em Nature of problem:} The structure factor of a molecule in intense laser fields determines its orientation-dependent tunneling ionization rate, which is crucial for the studies of ultrafast molecular dynamics and its control. However, the strong-field community lacks an open-source code to calculate the molecular structure factor, and can only resort to known results of a few molecules. \\
{\em Solution method:} We develope the \texttt{PyStructureFactor} program with the structure factor of arbitrary molecules calculated using the weak-field asymptotic theory in the integral representation. The underlying electronic structure necessary for the calculation is obtained using the \texttt{PySCF} quantum chemistry package. \\
{\em Restrictions on the Accuracy:} The accuracy of the molecular structure factor calculated by \texttt{PyStructureFactor} is restricted by the level of precision of the electronic structure information extracted from the \texttt{PySCF} package. \\
\cyan{{\em Running time:} The running time depends on the size of the molecule and the basis set of the SCF calculation and other parameters passed to the program. The example in Fig.~\ref{fig:code_example} took 1.2 sec. to finish on an AMD Ryzen 9 7950X CPU on the WSL Ubuntu 22.04 LTS.}
\end{small}

@@

Advances in the laser technology have made intense laser fields widely accessible in typical table-top lab settings. When matter interacts with intense laser fields, a plethora of novel strong-field phenomena emerge that are of fundamental interest, such as high-order harmonic generation (HHG) \cite{krause_high_1992,corkum_plasma_1993,popmintchev_the_2010}, above-threshold ionization \cite{agostini_free_1979,becker_above_2002,milosevic_above_2006}, nonsequential double ionization \cite{walker_precision_1994}, and laser-induced electron diffraction \cite{blaga_imaging_2012,wolter_ultrafast_2016}. HHG is the key to the generation of extreme ultraviolet laser pulses, which has facilitated the improvement of time resolution of ultraprecise measurements down to the attosecond level \cite{krausz_attosecond_2009,dahlstroem_introduction_2012,pazourek_attosecond_2015,kheifets_wigner_2023}. Common to many of these strong-field phenomena is their first step, known as tunneling ionization \cite{keldysh_ionization_1965,chin_from_2004}, which is thus a cornerstone of strong-field and attosecond science. It has attracted widespread interest not only in physics but also in chemistry and related fields. Given the recent development in optochemistry \cite{li_light_2022,ma_transient_2021}, a complementary emerging field to photochemistry, the importance of the tunneling ionization of molecules has been elevated to new heights.

In contrast to photoionization where the laser is manifested as photons in the frequency domain, tunneling ionization is better represented by the highly nonlinear ionization induced by intense optical fields in the time domain $F(t)$, with a tunneling ionization rate \cite{ammosov_tunnel_1986,delone_tunneling_1998}
\begin{equation}
    W[F(t)] \sim \ee^{-2\kappa^3/3F(t)}
    \label{eq:FieldFactor}
\end{equation}
depending exponentially on the field strength $F(t)$, where $\kappa=\sqrt{-2E_0}$ with $E_0$ \cyan{the orbital energy of the target}. For typical intense infrared laser fields, the photon energy is substantially lower than the ionization potential of the bound electron. Moreover, the timescale of the field oscillation is much longer than the intrinsic attosecond timescale of the bound electron. Therefore, the strong-field ionization process can be approximated by tunneling in a static electric field represented by the instantaneous laser electric field $F(t)$ \cite{tolstikhin_adiabatic_2010, tolstikhin_adiabatic_2012}.

@@

In this work, an open-source program implementing WFAT in the integral representation is developed that can easily and quickly calculate the molecular structure factor of common molecules. In our implementation, named the \texttt{PyStructureFactor}, the ionizing molecular orbital is expanded as a linear combination of GTOs at the HF level of theory calculated by the \texttt{PySCF} package \cite{sun_pyscf_2018, sun_recent_2020}. The integrals are evaluated numerically using a three-dimensional grid-based method, which exhibits much better numerical stability and is readily applicable to large molecules, compared to the standard analytical integration procedure. Our present implementation of \texttt{PyStructureFactor} features \cout{high accuracy and} efficient computation towards the calculation of the molecular structure factor.

@@

        \texttt{move\_dip\_zero}    & Indicates whether to shift the molecular coordinates such that its dipole moment \cyan{[Eq. (\ref{eq:ParentIonDipole})]} vanishes

>>>>

{\bf \noindent PROGRAM SUMMARY} \\
\begin{small}
\noindent
{\em Program Title:} PyStructureFactor \\
{\em CPC Library link to program files:} (to be added by Technical Editor) \\
{\em Developer's repository link:} \url{https://github.com/TheStarAlight/PyStructureFactor} \\
{\em Code Ocean capsule:} (to be added by Technical Editor) \\
{\em Licensing provisions:} Apache-2.0 \\
{\em Programming language:} Python 3                                  \\
{\em Supplementary material:}                                 \\
{\em Nature of problem:} The structure factor of a molecule in intense laser fields determines its orientation-dependent tunneling ionization rate, which is crucial for the studies of ultrafast molecular dynamics and its control. However, the strong-field community lacks an open-source code to calculate the molecular structure factor, and can only resort to known results of a few molecules. \\
{\em Solution method:} We develope the \texttt{PyStructureFactor} program with the structure factor of arbitrary molecules calculated using the weak-field asymptotic theory in the integral representation. The underlying electronic structure necessary for the calculation is obtained using the \texttt{PySCF} quantum chemistry package. \\
{\em Restrictions on the Accuracy:} The accuracy of the molecular structure factor calculated by \texttt{PyStructureFactor} is restricted by the level of precision of the electronic structure information extracted from the \texttt{PySCF} package. \\
\cyan{{\em Running time:} The running time depends on the size of the molecule, the basis set of the calculation, the level of precision of the electronic structure calculations, and other parameters passed to the program. The example in Fig.~\ref{fig:code_example} took 1.2 seconds to finish on an AMD Ryzen 9 7950X CPU on the WSL Ubuntu 22.04 LTS.}
\end{small}

@@

Advances in the laser technology have made intense laser fields widely accessible in typical table-top lab settings. When matter interacts with intense laser fields, a plethora of novel strong-field phenomena emerge that are of fundamental interest, such as high-order harmonic generation (HHG) \cite{krause_high_1992,corkum_plasma_1993,popmintchev_the_2010}, above-threshold ionization \cite{agostini_free_1979,becker_above_2002,milosevic_above_2006}, nonsequential double ionization \cite{walker_precision_1994}, and laser-induced electron diffraction \cite{blaga_imaging_2012,wolter_ultrafast_2016}. HHG is the key to \cyan{produce extreme ultraviolet light pulses}, which has facilitated the improvement of time resolution of ultraprecise measurements down to the attosecond level \cite{krausz_attosecond_2009,dahlstroem_introduction_2012,pazourek_attosecond_2015,kheifets_wigner_2023}. Common to many of these strong-field phenomena is their first step, known as tunneling ionization \cite{keldysh_ionization_1965,chin_from_2004}, which is thus a cornerstone of strong-field and attosecond science. It has attracted widespread interest not only in physics but also in chemistry and related fields \cyan{\cite{smirnova_attosecond_2009,sukiasyan_exchange_2010,xie_attosecond-recollision-controlled_2012,spanner_strong-field_2012,doblhoff-dier_classical_2013,doblhoff-dier_theoretical_2016,patchkovskii_full-dimensional_2017}}. Given the recent development in optochemistry \cite{li_light_2022,ma_transient_2021}, a complementary emerging field to photochemistry, the importance of the tunneling ionization of molecules has been elevated to new heights.

In contrast to photoionization where the \cyan{photonic feature of light plays a dominant role}, tunneling ionization is better represented by the highly nonlinear ionization induced by intense optical fields in the time domain $F(t)$, with a tunneling ionization rate \cite{ammosov_tunnel_1986,delone_tunneling_1998}
\begin{equation}
    W[F(t)] \sim \ee^{-2\kappa^3/3F(t)}
    \label{eq:FieldFactor}
\end{equation}
depending exponentially on the field strength $F(t)$, where $\kappa=\sqrt{-2E_0}$ with $E_0$ \cyan{the orbital energy of the target}. For typical intense infrared laser fields, the photon energy is substantially lower than the ionization potential of the bound electron. Moreover, the timescale of the field oscillation is much longer than the intrinsic attosecond timescale of the bound electron. Therefore, the strong-field ionization process can be approximated by tunneling in a static electric field represented by the instantaneous laser electric field $F(t)$ \cite{tolstikhin_adiabatic_2010, tolstikhin_adiabatic_2012}.

@@

In this work, an open-source program implementing WFAT in the integral representation is developed that can easily and quickly calculate the molecular structure factor of common molecules. In our implementation, named the \texttt{PyStructureFactor}, the ionizing molecular orbital is expanded as a linear combination of GTOs at the HF level of theory calculated by the \texttt{PySCF} package \cite{sun_pyscf_2018, sun_recent_2020}. The integrals are evaluated numerically using a three-dimensional grid-based method, which exhibits much better numerical stability and is readily applicable to large molecules, compared to the standard analytical integration procedure. Our present implementation of \texttt{PyStructureFactor} features \cyan{flexible control of accuracy and} efficient computation towards the calculation of the molecular structure factor.

@@

        \texttt{move\_dip\_zero}    & Indicates whether to shift the molecular coordinates such that its dipole moment \cyan{[Eq.~(\ref{eq:ParentIonDipole})]} vanishes
